---
title: "R for Data Science"
output: html_document
---

```{r}
library("tidyverse")
```

# Chapter 1: Data Visualization with ggplot2

## A Graphing Template

```{r}
# 1. Run ggplot(data = mpg). What do you see?
ggplot(data = mpg)
```

Is jut a gray rectangle.

```{r}
# 2. How many rows are in mtcars? How many columns?
nrow(mtcars)
ncol(mtcars)
```

mtcars has 32 rows and 11 columns.

```{r}
# 3. What does the drv variable describe? Read the help for ?mpg to find out.
?mpg
```

The traction of the car, f if is a front-wheel drive,
r if is a rear-wheel drive, and 4 for a 4wd.

```{r}
# 4. Make a scatterplot of hwy versus cyl.
ggplot(data = mpg) +
  geom_point(mapping = aes(x = hwy, y = cyl))
```

```{r}
# 5. What happens if you make a scatterplot of class versus drv? Why is the plot not useful?
ggplot(data = mpg) +
  geom_point(mapping = aes(x = class, y = drv))
```

Class and drv don't contain numerical data, they have catergorical data. It just tells where both categories meet. 

## Aesthetic Mappings

```{r}
# 1. What’s gone wrong with this code? Why are the points not blue?
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, 
                           color = "blue")
             )
```

color = "blue" should be outside the aes().

```{r}
# 2. Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset.) How can you see this information when you run mpg?
?mpg
mpg
```

Categorical: manufacturer model, trans, drv, fl, class.
Continuous: displ, year, cyl, city, hwy.
Categorical variables are a chr datatype and continuous variables are a int.

```{r}
# 3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical versus contin‐ uous variables?
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy,
                           color = year, 
                           size = cyl))
```
A continuous variable can not be mapped to shape.

```{r}
# Take the first faceted plot in this section:
        ggplot(data = mpg) +
          geom_point(mapping = aes(x = displ, y = hwy)) +
          facet_wrap(~ class, nrow = 2)
# What are the advantages to using faceting instead of the color aesthetic? What are the disadvantages? How might the balance change if you had a larger dataset?
```

Is easier to read each variable. It is harde to compare across variables. 

```{r}
# 5. Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?
?facet_wrap
```

Number of rows and columns. 

```{r}
# 6. When using facet_grid() you should usually put the variable with more unique levels in the columns. Why?
```

The breaks in the y axis would shrink making it harder to see which values are being mapped.

## Geometric Objects

```{r}
# 1. What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?
```
line, boxplot, histogram, area.

```{r}
# 2. Run this code in your head and predict what the output will look like. Then, run the code in R and check your predictions:
        ggplot(
          data = mpg,
          mapping = aes(x = displ, y = hwy, color = drv)
)+
geom_point() + geom_smooth(se = FALSE)
```

```{r}
# 3. What does show.legend = FALSE do? What happens if you remove it? Why do you think I used it earlier in the chapter?
```

It removes the little box that specifies the grouping. 

```{r}
# 4. What does the se argument to geom_smooth() do?
```

It shows a shadowed area.

```{r}
# 5. Will these two graphs look different? Why/why not?
       ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
         geom_point() +
         geom_smooth()
       ggplot() +
         geom_point(
data = mpg,
mapping = aes(x = displ, y = hwy) )+
         geom_smooth(
           data = mpg,
           mapping = aes(x = displ, y = hwy)
)
```

No, they will look the same.

```{r}
# 6. Re-create the R code necessary to generate the following graphs.
ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point() +
  geom_smooth(se = FALSE)

ggplot(data = mpg, aes(x = displ, y = hwy, group = drv)) +
  geom_point() +
  geom_smooth(se = FALSE)

ggplot(data = mpg, aes(x = displ, y = hwy, color = drv)) +
  geom_point() +
  geom_smooth(se = FALSE)

ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = drv)) +
  geom_smooth(se = FALSE)

ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = drv)) +
  geom_smooth(se = FALSE, aes(group = drv))

ggplot(data = mpg, aes(x = displ, y = hwy)) +
  geom_point(aes(color = drv))
```

## Statistical Transformations

```{r}
# 1. What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?

ggplot(data = diamonds) +
  geom_boxplot(mapping = aes(x = cut, y = depth))
```

min, max, mean. 

```{r}
# 2. What does geom_col() do? How is it different to geom_bar()?
?geom_col
```

In geom_bar, the height of the bar is proportional to the number of cases in each group. In geom_col, the height of the bar represents values in the data.

```{r}
# 3. Most geoms and stats come in pairs that are almost always used in concert. Read through the documentation and make a list of all the pairs. What do they have in common?
```

```{r}
# 4. What variables does stat_smooth() compute? What parameters control its behavior?
?stat_smooth
```

It computes conditional means. It has many parameters like mapping, data, position, aesthetic mappings, etc.

```{r}
# 5. In our proportion bar chart, we need to set group = 1. Why? In other words what is the problem with these two graphs?
        ggplot(data = diamonds) +
          geom_bar(mapping = aes(x = cut, y = ..prop.., group = 1))
        ggplot(data = diamonds) +
          geom_bar(
            mapping = aes(x = cut, fill = color, y = ..prop..)
          )
```

If we don't specify group = 1, it treats all the groups as different groups instead of 1 group.

## Position Adjustments

```{r}
# 1. What is the problem with this plot? How could you improve it?
        ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
          geom_point()
```

With geom_jitter.

```{r}
# 2. What parameters to geom_jitter() control the amount of jit‐ tering?
?geom_jitter
```

width and height.

```{r}
# 3. Compare and contrast geom_jitter() with geom_count().
?geom_count()
```

geom_jitter works with discrete data.

```{r}
# 4. What’s the default position adjustment for geom_boxplot()?
# Create a visualization of the mpg dataset that demonstrates it.
```

position_dodge

## Coordinate Systems

```{r}
# 1. Turn a stacked bar chart into a pie chart using coord_polar().
bar <- ggplot(data = diamonds) +
geom_bar(mapping = aes(x = cut, fill = cut))
bar + coord_polar()
```

```{r}
# 2. What does labs() do? Read the documentation.
?labs
```

Modifies axis, legend, and plot labels.

```{r}
# 3. What’s the difference between coord_quickmap() and coord_map()?
```

coord_map can use a variety of projections.

```{r}
# 4. What does the following plot tell you about the relationship between city and highway mpg? Why is coord_fixed() impor‐ tant? What does geom_abline() do?
        ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
          geom_point() +
  geom_abline() +
  coord_fixed()
```

Vehicles with low cty mileage have a low hwy mileage and the opposite is also true. coord_fixed makes the x axis narrower. geom_abline adds a best fit line to the plot.


# Chapter 2: Workflow: Basics

```{r}
# 1. Why does this code not work?
my_variable <- 10
my_varıable
#> Error in eval(expr, envir, enclos): #> object 'my_varıable' not found
```

When calling the variable, the 'i' was replaced by a similar symbol.

```{r}
# 2. Tweak each of the following R commands so that they run correctly:
   library(tidyverse)
       ggplot(data = mpg) +
         geom_point(mapping = aes(x = displ, y = hwy))
filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```

```{r}
# 3. Press Alt-Shift-K. What happens? How can you get to the same place using the menus?
```

A keyboard shortcut quick reference pops up. You can also find it in the tools menu.